\section{Introduction}
\label{sec-intro}

Alice was beginning to get very tired of sitting by her sister on the
bank, and of having nothing to do: once or twice she had peeped into
the book her sister was reading, but it had no pictures or
conversations in it, 'and what is the use of a book,' thought Alice
'without pictures or conversations?'

So she was considering in her own mind (as well as she could, for the
hot day made her feel very sleepy and stupid), whether the pleasure
of making a daisy-chain would be worth the trouble of getting up and
picking the daisies, when suddenly a White Rabbit with pink eyes ran
close by her.

There was nothing so VERY remarkable in that; nor did Alice think it
so VERY much out of the way to hear the Rabbit say to itself, 'Oh
dear!
Oh dear!
I shall be late!'
(when she thought it over afterwards, it occurred to her that she
ought to have wondered at this, but at the time it all seemed quite
natural); but when the Rabbit actually TOOK A WATCH OUT OF ITS
WAISTCOAT-POCKET, and looked at it, and then hurried on, Alice
started to her feet, for it flashed across her mind that she had
never before seen a rabbit with either a waistcoat-pocket, or a watch
to take out of it, and burning with curiosity, she ran across the
field after it, and fortunately was just in time to see it pop down a
large rabbit-hole under the hedge.

\myparagraph{Our Contribution}

Needs to be completed, but might cite some things by name perhaps
including {\citet{zm06compsurv}}, though some things will more
naturally be ``end of sentence''-type references {\citep{wmb99mg}}.
Note the use of the strings in the bibtex file to cover all
conference and journal names, make sure they get used.
And make sure that {\verb+\citeauthor+} and {\verb+\citet+} get used
when author names are required in the text, so that names get the
correct spelling.
And, note also the use of initials-only in the file
{\verb+local.bib+}, don't let any full names go in there, because
there will be a space-saving squeeze applied to every paper before
the submission.
Note also that this is using {\verb+natbib+}; the ACM bib style
doesn't do a very good job of re- and de-capitalizing words in paper
titles.

Consistency is everything!

\myparagraph{Leaving Tracks}

It's nice to be able to leave notes through the manuscript as it
develops.
\todo{Like, reminders of things still needing attention.}

\alistair{Might also include some comments from people.}
\alicia{Yes, I agree, it might.}
\andrew{I never agree with Alistair.}
